### 2010-02-26 byu_studies/poster.tex
First pass of the poster done, still a ways to go

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\typeout{Poster Starts}
\background{
  \begin{tikzpicture}[remember picture,overlay]%
    \draw (current page.north west)+(-2em,-0em) node[anchor=north west] {\hspace{-2em}\includegraphics[height=1.1\textheight]{silhouettes_background}};
  \end{tikzpicture}%
}
\definecolor{silver}{cmyk}{0,0,0,0.3}
\definecolor{yellow}{cmyk}{0,0,0.9,0.0}
\definecolor{blue}{cmyk}{0.9,0,0,0.0}
\definecolor{reddishyellow}{cmyk}{0,0.22,1.0,0.0}
\definecolor{reddishblue}{cmyk}{1,0.22,0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}
\definecolor{darkYellow}{cmyk}{0,0,1.0,0.5}
\definecolor{darkSilver}{cmyk}{0,0,0,0.1}

\definecolor{lightyellow}{cmyk}{0,0,0.3,0.0}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
\definecolor{lightblue}{cmyk}{.3,0,0,0.0}
\definecolor{lighterblue}{cmyk}{.1,0,0,0.0}
\definecolor{lightestblue}{cmyk}{.05,0,0,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighterblue,
  bgColorTwo=lightestblue,
  borderColor=reddishblue,
  headerColorOne=blue,
  headerColorTwo=reddishblue,
  headerFontColor=black,
  boxColorOne=lightblue,
  boxColorTwo=lighterblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Automatic Topic Discovery in 100 Years of General Conference Talks}
  % Authors
  {\sf %Sans Serif
  % Serif
  Matthew Gardner
  (mjg82@byu.edu)
  and
  Eric Ringger
  (ringger@cs.byu.edu)
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    \includegraphics[height=5.5em]{logo}
  \end{minipage}}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Contribution}{name=contribution,column=0,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   {}We use state of the art natural language processing techniques to gain new
   insights from 100 years of General Conference Talks.  Using computers to
   sift through a corpus that would be overwhelmingly large to process
   manually, we can discover relationships between talks and trends over time
   that help us to better appreciate the trove of knowledge in these inspired
   discourses.
 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Methodology}{name=methodology,column=0,below=contribution}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	Document clustering is the task of determining which documents are similar
	to each other in any given corpus.  The fundamental assumption made by
	clustering techniques is that there are several topics used in the corpus,
	and each document is generated by a single (unknown) topic.  Given a
	clustering model and a set of documents, statistical methods can be used to
	determine the best clustering of documents for that corpus.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Expression Neutralization}{name=results neutralization,column=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}@{ }@{ }c@{ }c@{ }c@{ }c@{ }}
    \includegraphics[height=0.42\linewidth]{16_1_tgt}&
    \includegraphics[height=0.42\linewidth]{16_1_expression}&
    \includegraphics[height=0.42\linewidth]{16_1_neutral}\\[-0.8em]
    \smaller a) Target & \smaller b) Fit & \smaller c) Normalized\\[0.8em]
    \includegraphics[height=0.42\linewidth]{16_6_tgt}&
    \includegraphics[height=0.42\linewidth]{16_6_expression}&
    \includegraphics[height=0.42\linewidth]{16_6_neutral}\\[-0.8em]
    \smaller a) Target & \smaller b) Fit & \smaller c) Normalized
  \end{tabular}
  Expression normalisation for two scans of the same individual.  
  The robust fitting gives a good estimate (b) of the true face surface given
  the noisy measurement (a). It fills in holes and removes artifacts using
  prior knowledge from the face model. The pose and expression normalized faces
  (c) are used for face recognition.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Robustness}{name=robustness,column=1,below=results neutralization,span=1,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
    \includegraphics[height=0.42\linewidth]{56_4_tgt}&
    \includegraphics[height=0.42\linewidth]{23_2_tgt}&
    \includegraphics[height=0.42\linewidth]{5_6_tgt}\\[-0.8em]
                       & \smaller a) Targets & \\[0.8em]
    \includegraphics[height=0.42\linewidth]{56_4_expression}&
    \includegraphics[height=0.42\linewidth]{23_2_expression}& 
    \includegraphics[height=0.42\linewidth]{5_6_expression}\\[-0.8em]
                    & \smaller b) Fits & 
  \end{tabular}
  The reconstruction (b) is robust against scans (a) with artifacts, noise, and
  holes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}{name=results,column=2,span=2,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{multicols}{2}
        The method was evaluated on the GavabDB expression dataset which
        contains 427 Scans, with 3 neutral scans and 4 expression scans per ID.
        To test the impact of expression invariance on neutral data we used the
        UND Dataset from the Face Recognition Great Vendor Test, which contains
        953 neutral scans with one to eight scans per subject.
      \end{multicols}\vspace{-1em}
      \mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
      \begin{tabular}{cc}
        \hspace{0.5em}\scalebox{0.74}{\input{shrec_MNCG}} &
        \hspace{0.5em}\scalebox{0.74}{\input{und_MNCG}}
      \end{tabular}\\
%      \begin{multicols}{2}
        {Expression neutralization improves results on the expression dataset
        without decreasing the accuracy on the neutral testset. Plotted is the
        ratio of correct answers to  the number of possible correct answers.
        %Note the different scales for the two graphs.
        %Our approach has a high accuracy on the neutral (UND) dataset.
%      \end{multicols}\vspace{-1em}
      \\\mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
      \begin{tabular}{cc}
        \hspace{0.5em}\scalebox{0.74}{\input{shrec_PR}} &
        \hspace{0.5em}\scalebox{0.74}{\input{und_PR}}
      \end{tabular}\\
%      \begin{multicols}{2}
        {Plotted are precision and recall for different retrieval depths. The lower
        precision of the UND database is due to the fact that some queries have no
        correct answers.}
%      \end{multicols}\vspace{-1em}
      \\\mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
      \begin{tabular}{cc}
        \hspace{0.5em}\scalebox{0.74}{\input{shrec_FARFRR}} &
        \hspace{0.5em}\scalebox{0.74}{\input{und_FARFRR}}
      \end{tabular}\\
%      \begin{multicols}{2}
        {Impostor detection is reliable, as the minimum distance to a match
        is smaller than the minimum distance to a nonmatch. }
%      \end{multicols}
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Open Questions}{name=questions,column=2,span=1,above=bottom,below=results}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    While the expression and identity space are linearly independent, there is
    some expression left in the identity model. This is because a ``neutral''
    face is interpreted differently by the subjects. We investigate the
    possibilty to build an identity/expression separated model without using
    the data labelling, based on a measure of independence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \smaller 
  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{References}{name=references,column=3,above=funding,below=results}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \smaller
    \vspace{-0.4em}
    \bibliographystyle{ieee}
    \renewcommand{\section}[2]{\vskip 0.05em}
      \begin{thebibliography}{1}\itemsep=-0.01em
      \setlength{\baselineskip}{0.4em}
      \bibitem{amberg07:nonrigid}
        B.~Amberg, S.~Romdhani, T. Vetter.
        \newblock {O}ptimal {S}tep {N}onrigid {ICP} {A}lgorithms for {S}urface {R}egistration
        \newblock In {\em CVPR 2007}
      \bibitem{amberg08:recognition}
        B.~Amberg, R.~Knothe, T. Vetter.
        \newblock Expression Invariant Face Recognition with a 3D Morphable Model
        \newblock In {\em AFGR 2008}
      \end{thebibliography}
\end{poster}%
%
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\typeout{Poster Starts}
\definecolor{blue}{cmyk}{0.9,0,0,0.0}
\definecolor{reddishblue}{cmyk}{1,0.22,0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}

\definecolor{lightblue}{cmyk}{.3,0,0,0.0}
\definecolor{lighterblue}{cmyk}{.2,0,0,0.0}
\definecolor{lightestblue}{cmyk}{.1,0,0,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighterblue,
  bgColorTwo=lightestblue,
  borderColor=reddishblue,
  headerColorOne=blue,
  headerColorTwo=reddishblue,
  headerFontColor=black,
  boxColorOne=lightblue,
  boxColorTwo=lighterblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
  background=shade-tb,
  %background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Automatic Topic Discovery in 100 Years of General Conference Talks}
  % Authors
  {\sf %Sans Serif
  % Serif
  Matthew Gardner
  (mjg82@byu.edu)
  and
  Eric Ringger
  (ringger@cs.byu.edu)
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    %\includegraphics[height=5.5em]{logo}
  \end{minipage}}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Contribution}{name=contribution,column=0,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   {}

   We use state of the art natural language processing techniques to gain new
   insights from 100 years of General Conference Talks.  Using computers to
   sift through a corpus that would be overwhelmingly large to process
   manually, we can discover relationships between talks and trends over time
   that help us to better appreciate the trove of knowledge in these inspired
   discourses.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Background and Methodology}
  {name=methodology,column=0,below=contribution}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	Document clustering is the task of determining which documents are similar
	to each other in any given corpus.  The fundamental assumption made by
	clustering techniques is that there are several topics used in the corpus,
	and each document is generated by a single (unknown) topic.  Given a
	clustering model and a set of documents, statistical methods can be used to
	determine the best clustering of documents for that corpus.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}
  {name=results word distributions,column=1,span=2,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	The main result of using LDA is a list of which words are most likely to be
	used in each topic.  In the algorithm, the topics just have numbers; the
	computer merely looks for statistical relationship between words.  The
	labels are thus our own.  We present here a few of the topics we found.

	\small
	\begin{center}
	  \begin{tabular}{ccccc}
		Topic 19: Tithing&Topic 33: Welfare&Topic 52: Women&Topic 37: Families
		&Topic 7: Government\\
		\hline
		tithing&welfare&women&children&government \\
		pay&poor&society&home&united \\
		money&church&relief&family&liberty \\
		debt&fast&sisters&parents&nation \\
		means&help&hinckley&teach&states \\
		out&services&each&child&country \\
		people&program&b&families&freedom \\
		one&plan&gordon&homes&land \\
		paid&care&lives&love&free \\
		poor&needs&service&mother&men \\
		tithes&food&sister&taught&constitution \\
		get&need&forward&fathers&people \\
		more&family&strength&responsibility&america \\
	  \end{tabular}
	\end{center}

	\normalsize
	\mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
	Because each talk has a date associated with it, we can use LDA to analyze
	the distribution of these topics over time, seeing at when certain topics
	were most discussed.  In doing this, we see clear correlations with
	real-world occurrences.

	\begin{center}
	  \includegraphics[height=.34\linewidth]{topic19.eps}
	  \includegraphics[height=.34\linewidth]{topic33.eps}

	  \includegraphics[height=.34\linewidth]{topic52.eps}
	  \includegraphics[height=.34\linewidth]{topic56.eps}
	\end{center}

  }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Future Work}{name=future work,column=3,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	We have used natural language processing techniques on a novel data
	source---LDS General Conference talks.  However, our exploration of the
	results has been quite preliminary.  Our research lays the groundwork for a
	more thorough analysis of religious discourse in the LDS Church.  These
	techniques allow us to quickly answer questions such as, ``Which topics are
	constant over time, and which come and go?'' and ``Which years had the
	highest diversity of topics, and which were more narrow-focused?''

	We also have only considered General Conference talks.  A fruitful avenue
	of future work would be to compare the results of our techniques on many
	different corpora of LDS religious and scholarly texts, such as the Journal
	of Discourses, the Book of Mormon, the Doctrine and Covenants, the
	collected works of Hugh Nibley, or the past 50 years of BYU Studies.  Such
	analysis could broaden our understanding of and appreciation for our
	textual history.

@@

\end{poster}%
%
\end{document}
